Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-02 neurips-20/cvx-flats.tex
Fixing subgradient def

\bo{I like all this, but maybe it can be reworded to flow better with the above?}
Flats of a convex (expected) loss are complemented by its subgradients\footnote{We define the subgradient $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$.}.  % of convex losses and their flats in order to understand convex elicitation complexity. 
While subgradients live in the prediction space and flats in probability space, the two can be connected considering a $p \in \simplex$.
In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \partial \exploss{L}{u}{p}$; our desired optimality condition.\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
The intuition for this result comes from the proof of~\citet[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound} through a much shorter proof thanks to our reliance on elicitation.

>>>>

\bo{I like all this, but maybe it can be reworded to flow better with the above?}
Flats of a convex (expected) loss are complemented by its subgradients.\footnote{We define the subdifferential $\partial L(u,y) = \{g \in \reals^d : L(u',y) \geq L(u,y) +g^T (u' - u) \; \forall u' \in \reals^d  \}$, and members of this set subgradients.}  % of convex losses and their flats in order to understand convex elicitation complexity. 
While subgradients live in the prediction space and flats in probability space, the two can be connected considering a $p \in \simplex$.
In a loose sense, this $p$ is a witness of a flat of the level set, and the flat must be of certain codimension (dependent on prediction dimension) so that, for this witness $p$, we can extract a witness $W$ of subgradient sets proving that $\vec 0 \in \partial \exploss{L}{u}{p}$; our desired optimality condition.\jessiet{This is probably TMI but it at least helped me to write it out and think of it this way (p as a witness of the flat, in a loose sense)}
The intuition for this result comes from the proof of~\citet[Theorem 16]{ramaswamy2016convex}, although indirect elicitation lets us simplify their proof that originally relied on calibration.
In fact, their main proof tool, the subspace of feasible dimensions (Definition~\ref{def:subspace-feas}), is a linear shift of a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}, which lets us deduce their result as Corollary~\ref{cor:fsd-bound} through a much shorter proof thanks to our reliance on elicitation.
